---
name: Dr.
surname: Paul Schmidt
profilepic: contactinfo/pic2.jpg
date: "`r format(Sys.time(), '%m/%Y')`"
qualifications: Dr. sci. agr.
position: Data Scientist / Biostatistician
address: Hamburg, Germany
phone: +49 172 3091577
email: schmidtpaul1989@outlook.com
linkedin: schmidtpaul1989
researchgate: Paul_Schmidt17
github: SchmidtPaul
headcolor: 414141
output: 
  vitae::awesomecv:
    keep_tex: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(RefManageR)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```

<!-- Overwrite the default footer to have 1/n page numbering: -->
\makecvfooter{`r format(Sys.time(), '%B, %Y')`}{Dr. Paul Schmidt~~~·~~~Curriculum Vitae}{\thepage/\pageref{LastPage}}

# Professional experience

```{r employment}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Data scientist", "BioMath - Applied Statistics and Informatics in Life Sciences", "Rostock & Hamburg, Germany", "Jan 2019 - Present", "Various statistical analyses from raw data to final report for e.g. yearly post-market monitoring (survey; agriculture), risk assessment (meta-analysis; epidemiology), a long-term field trial (experiment; environment), geographic distribution (geospatial; administrative office)",
  "Data scientist", "BioMath - Applied Statistics and Informatics in Life Sciences", "Rostock & Hamburg, Germany", "Jan 2019 - Present", "Implement new / streamline existing SOPs (for e.g. systematic literature reviews and meta-analyses) by making better use of in-depth functionality of established software and additionally via introducing complementing software/tools",
  "Data scientist", "BioMath - Applied Statistics and Informatics in Life Sciences", "Rostock & Hamburg, Germany", "Jan 2019 - Present", "Supervise project communication and time management",
  "Data scientist", "BioMath - Applied Statistics and Informatics in Life Sciences", "Rostock & Hamburg, Germany", "Jan 2019 - Present", "Conduct in-depth research,  write scientific reports and proofread especially English tender application, report and publication drafts",
  "Workshop Instructor", "Freelancer (part-time)", "see 'Teaching' section below", "Nov 2018 - Present", "Develop and teach workshops on statistics in R; specific content and language according to the contractor",
  "Workshop Instructor", "Freelancer (part-time)", "see 'Teaching' section below", "Nov 2018 - Present", "Provide corresponding material on my websites (see 'Other skills' section below)",
  "Research associate ", "University of Hohenheim", "Stuttgart, Germany", "Sep 2015 - Dec 2018", "Personalized consulting (ranging from single-appointment to project-accompanying) for students and research associates in terms of experimental design, data handling, statistical analyses and/or presentation of results",
  "Research associate ", "University of Hohenheim", "Stuttgart, Germany", "Sep 2015 - Dec 2018", "Develop, conduct and manage yearly statistical analysis of yield stability data for external company",
  "Research associate ", "University of Hohenheim", "Stuttgart, Germany", "Sep 2015 - Dec 2018", "Develop, organize and teach workshops in statistics, R and SAS",
  "Research associate ", "University of Hohenheim", "Stuttgart, Germany", "Sep 2015 - Dec 2018", "Supervise student writing his MSc thesis",
  "Junior Data scientist", "BioMath - Applied Statistics and Informatics in Life Sciences", "Rostock, Germany", "Jan 2015 - Aug 2015", "Streamline statistical analyses of monitoring data",
  "Junior Data scientist", "BioMath - Applied Statistics and Informatics in Life Sciences", "Rostock, Germany", "Jan 2015 - Aug 2015", "Implement SOP for systematic literature reviews",
) %>% 
  detailed_entries(role, dates, company, loc, details)
```

# Education

```{r education}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "Dr. sc. agr.", "University of Hohenheim", "Stuttgart, Germany", "Sep 2015 - Nov 2019", "DFG-funded PhD student in the biostatistics unit of Prof. Dr. Hans-Peter Piepho",
  "Dr. sc. agr.", "University of Hohenheim", "Stuttgart, Germany", "Sep 2015 - Nov 2019", "Cumulative doctoral thesis: 'Estimating heritability in plant breeding programs' graded 'magna cum laude'",
  "Visiting PhD student", "Purdue University", "West Lafayette, IN, USA", "Sep 2015 - Dec 2015", "Visiting PhD student in the statistical bioinformatics unit of Prof. Dr. Rebecca Whitbeck Doerge",
  "Visiting PhD student", "Purdue University", "West Lafayette, IN, USA", "Sep 2015 - Dec 2015", "Arranged on personal initiative, this collaboration allowed for scientific exchange and inspiration at the beginning of my PhD",
  "MSc Crop Science: Plant Breeding", "University of Hohenheim", "Stuttgart, Germany", "Oct 2012 - Dec 2014", "Specialization in biostatistics and plant breeding (final grade 1.4)",
  "MSc Crop Science: Plant Breeding", "University of Hohenheim", "Stuttgart, Germany", "Oct 2012 - Dec 2014", "MSc Thesis: 'Statistical Evaluation and Analysis of PACTS trials as a series of on-farm strip trials without replicates' graded 1.0",
  "BSc Agribiology (in german)", "University of Hohenheim", "Stuttgart, Germany", "Oct 2009 - Sep 2012", "Specialization in plant sciences and genetics (final grade 1.9)",
  "BSc Agribiology (in german)", "University of Hohenheim", "Stuttgart, Germany", "Oct 2009 - Sep 2012", "BSc Thesis: 'Cumulative effects of glyphosate trace concentrations during root exposition of winter wheat' graded 1.0",
  "Student exchange year", "Alexander Central High School", "Taylorsville, NC, USA", "Aug 2006 - Jul 2007", "Completed senior year and obtained high school diploma") %>% 
  detailed_entries(degree, dates, uni, loc, details)
```

# Other skills

\begin{cvskills}

  \cvskill  {General}
  {collaboration, communication, structure, time management, strategic oversight, problem solving} 
  
  \cvskill  {Languages}
  {German (native), English (effective operational proficiency)}
  
  \cvskill  {Software}
  {R, SAS, SPSS, ASReml, Excel, Word, PowerPoint, Citavi, Adobe Acrobat Pro, Latex, C\#, SQL} 
  
  \cvskill  {Statistics}
  {(generalized) linear (mixed) models, exploratory \& descriptive data analysis, experimental design} 
  
  \cvskill  {Presentation}
  {data visualization, data analysis reports, scientific publications, presentations} 
  
  \cvskill{Websites}{https://schmidtpaul.github.io/MMFAIR/0contactinfo.html}

\end{cvskills}

# Teaching

\begin{cvhonors}

\cvhonor
    {Instructor  }
    {Data science for experimental life sciences with R (part 2)}
    {Thünen Inst. Braunschweig (via zoom), 3d}
    {Mar 2022  } 
    
  \cvhonor
    {Instructor  }
    {Data science for experimental life sciences with R (part 2)}
    {Thünen Inst. Braunschweig (via zoom), 3d}
    {Mar 2022  } 
    
  \cvhonor
    {Instructor  }
    {Data science for experimental life sciences with R (part 1)}
    {Thünen Inst. Braunschweig (via zoom), 3d}
    {Mar 2022  } 

  \cvhonor
    {Instructor  }
    {Data science for experimental life sciences with R (part 1)}
    {Thünen Inst. Braunschweig (via zoom), 3d}
    {Mar 2022  } 

  \cvhonor
    {Instructor  }
    {Statistics with R (Beginner)}
    {Kassel Univ., 4d}
    {Dec 2021  }  

  \cvhonor
    {Instructor  }
    {Data science for life sciences with R (part 2)}
    {Thünen Inst. Braunschweig (via zoom), 3d}
    {Jul 2021  } 
    
  \cvhonor
    {Instructor  }
    {Data science for life sciences with R (part 1)}
    {Thünen Inst. Braunschweig (via zoom), 3d}
    {May 2021  } 

  \cvhonor
    {Instructor  }
    {Data science for life sciences with R (part 2)}
    {Thünen Inst. Braunschweig (via zoom), 3d}
    {Mar 2021  } 

  \cvhonor
    {Instructor  }
    {Planning exp. designs, rep. measures, and their analyses in R}
    {Kassel Univ. (via zoom), 2d}
    {Nov 2020  }
    
  \cvhonor
    {Instructor  }
    {Data science for life sciences with R (part 1)}
    {Thünen Inst. Braunschweig (via zoom), 3d}
    {Nov 2020  } 
    
  \cvhonor
    {Instructor  }
    {Experimental Design - Practicals in R}
    {CIHEAM Zaragoza (via zoom), 2d}
    {Oct 2020  }

  \cvhonor
    {Instructor  }
    {Real-time consultation on statistics and mixed models in R}
    {Kassel Univ., 2d}
    {Mar 2020  }
    
  \cvhonor
    {Instructor  }
    {Basics of applied statistics}
    {Rostock Univ., 2d}
    {Dec 2019  }
  
  \cvhonor
    {Instructor  }
    {Data science for life sciences with R (part 2)}
    {Thünen Inst. Braunschweig, 3d}
    {Nov 2019  }    

  \cvhonor
    {Instructor  }
    {Data science for life sciences with R (part 1)}
    {Thünen Inst. Braunschweig, 3d}
    {Oct 2019  }      

  \cvhonor
    {Instructor  }
    {Essential basics of statistics}
    {Rostock Univ., 2d}
    {Sep 2019  }  

  \cvhonor
    {Instructor  }
    {Mixed models with R}
    {Thünen Inst. Braunschweig, 3d}
    {Nov 2018  }  
    
  \cvhonor
    {Instructor  }
    {Implementation of yield stability assessment with ASReml-R}
    {Bangladesh Rice Research Inst., Gazipur, 3h}
    {May 2018  }
    
  \cvhonor
    {Instructor  }
    {Statistical analysis with SAS (monthly)}
    {Univ. of Hohenheim, Stuttgart, 3d}
    {2016-2018  }
    
  \cvhonor
    {Instructor  }
    {Statistical analysis with R (monthly)}
    {Univ. of Hohenheim, Stuttgart, 3d}
    {2016-2018  }
    
  \cvhonor
    {Teaching Assistant  }
    {Biometrics / Statistics (weekly)}
    {Univ. of Hohenheim, Stuttgart, 4h}
    {2016-2018  }
        
\end{cvhonors}

# Scientific publications

\footnotesize

```{r research-papers}
vitae::bibliography_entries("contactinfo/publications.bib") %>%
  select(-publisher, -`publisher-place`, -genre, -`title-short`) %>% 
  replace(is.na(.), "-") %>% 
  arrange(desc(issued), id)
```

